Optimal Task Phasing for End-To-End Latency in Harmonic Systems and Semi-Harmonic Automotive Systems

### 2024-09-27 paper.tex
structure of harmonic section
move hyperperiod lemma to the front

%% THEOREMS:
% Theorems --
\usepackage{amsthm}

@@

@@

	To achieve complex functionalities, usually several tasks have to cooperate. 
	A sequence of cooperating tasks is called a cause-effect chain $E=(\tau_1 \to \dots \to \tau_n)$ with $n\in \Nbb_{\geq 1}$.
	Specifically, data that is written by $\tau_i$ is read by $\tau_{i+1}$, for $i=1, \dots, n-1$.
	The underlying functionality is achieved when data has been propagated through all $n$ tasks. 
	\mario{I think we need a simple application-oriented example here}

@@

@@

	\mario{HERE}

	\begin{lemma}\label{lem:key_lemma}
		Let $\tau_p$ be the task with the highest period of $E$, i.e., $T_{\tau_p} = \max_{i=1, \dots, n} T_{\tau_i}$.
		If $\Tbb_E$ is max-harmonic, then 
		\begin{equation}
			\ell(\pc^p_{W_p}) 
			= \ell(\pc^p_{W_p+1}) 
			= \ell(\pc^p_{W_p+2})
			= \dots 
		\end{equation}
		In particular,  
		\begin{math}
			\lat(E) = \ell(\pc^p_{W_p}) 
		\end{math}
		holds.
	\end{lemma}

	\begin{proof}
		Let $m\geq W_p$.
		In the following we show that $\ell(\pc^p_{m}) 
		= \ell(\pc^p_{m+1})$.
	%
		By definition, $\pc^p_m = (\bc_m, \fc_{m+1})$ and $\pc^p_{m+1} = (\bc_{m+1}, \fc_{m+2})$.
		We start by investigating the immediate backward job chains, denoted as 
		$\bc_m = (\tau_1(j_1) \to\dots\to \tau_p(j_p))$ and $\bc_{m+1} = (\tau_1(\tilde{j}_1) \to\dots\to \tau_p({\tilde{j}}_p))$.
		By induction, we show that the jobs of both immediate backward job chains are exactly $T_{\tau_p}$ time units apart, or equivalently
		\begin{equation}\label{eq:induction1}
			j_i + \frac{T_{\tau_p}}{T_{\tau_i}} = \tilde{j}_i
		\end{equation}
		for all $i=p, p{-}1, \dots, 1$.

@@

>>>>

%% THEOREMS:
% Theorems --
\usepackage{amsthm}
\usepackage{thmtools,thm-restate}

@@

% \declaretheorem[sibling=lemma,name=Lemma]{repeatablelemma}

@@

	To achieve complex functionalities, usually several tasks have to cooperate. 
	A sequence of cooperating tasks is called a cause-effect chain 
	\begin{equation}
		E=(\tau_1 \to \dots \to \tau_n)
	\end{equation}
	with $n\in \Nbb_{\geq 1}$.
	Specifically, data that is written by $\tau_i$ is read by $\tau_{i+1}$, for $i=1, \dots, n-1$.
	The underlying functionality is achieved when data has been propagated through all $n$ tasks. 
	For this work, we denote by 
	\begin{equation}
		\Tbb_E := \setof{\tau_1, \dots, \tau_n} \subseteq \Tbb
	\end{equation}
	the tasks of $\Tbb$ that are part of the cause-effect chain.
	Furthermore, we assume that $\tau_i \neq \tau_j$ for all $i \neq j$.

	\mario{I think we need a simple application-oriented example with a picture here.}

@@

	Furthermore, for periodic tasks under LET, the read- and write-events repeat every hyperperiod $\lcm(T_{\tau_1}, \dots, T_{\tau_n})$ of $\Tbb_E$.
	Therefore, the partitioned job chains repeat every hyperperiod and only finitely many partitioned job chains need to be considered for the computation of the end-to-end latency.

	\begin{restatable}{lemma}{lemmarepetetive}\label{lem:repetitive}
		Let $\mu(p) := \frac{H}{T_{\tau_p}}$ be the number of periods of $\tau_p$ that fit into one hyperperiod $H:= \lcm(T_{\tau_1}, \dots, T_{\tau_n})$ of $\Tbb_E$.
		We have
		\begin{equation}
			\ell(\pc^p_{m}) 
			= \ell\left(\pc^p_{m+\mu(p)}\right)
		\end{equation}
		for all $m \geq W_p$.
		In particular,  
		\begin{equation}
			\lat(E) = \max\left( \ell\left(\pc^p_{W_p}\right), \dots, \ell\left(\pc^p_{W_p+\mu(p)-1}\right) \right)
		\end{equation}
		holds.
	\end{restatable}

	While it is easy to convince ourselves that this lemma holds, the proof requires technical details and is moved to the \hyperref[sec:appendix]{Appendix} for readability.

@@

	\begin{lemma}\label{lem:key_lemma}
		Let $\tau_p$ be the task with the highest period of $E$, i.e., $T_{\tau_p} = \max_{i=1, \dots, n} T_{\tau_i}$.
		If $\Tbb_E$ is max-harmonic, then 
		\begin{equation}
			\lat(E) = \ell(\pc^p_{W_p}) 
		\end{equation}
		holds.
	\end{lemma}

	\begin{proof}
		\mario{use Lemma~\ref{lem:repetitive}}
	\end{proof}

@@

\appendix
\label{sec:appendix}

We prove Lemma~\ref{lem:repetitive} from page \pageref{lem:repetitive}:

\lemmarepetetive*

\begin{proof}
	\mario{Proof to be adjusted to account for hyperperiod}

	Let $m\geq W_p$.
	In the following we show that $\ell(\pc^p_{m}) 
	= \ell(\pc^p_{m+1})$.
%
	By definition, $\pc^p_m = (\bc_m, \fc_{m+1})$ and $\pc^p_{m+1} = (\bc_{m+1}, \fc_{m+2})$.
	We start by investigating the immediate backward job chains, denoted as 
	$\bc_m = (\tau_1(j_1) \to\dots\to \tau_p(j_p))$ and $\bc_{m+1} = (\tau_1(\tilde{j}_1) \to\dots\to \tau_p({\tilde{j}}_p))$.
	By induction, we show that the jobs of both immediate backward job chains are exactly $T_{\tau_p}$ time units apart, or equivalently
	\begin{equation}\label{eq:induction1}
		j_i + \frac{T_{\tau_p}}{T_{\tau_i}} = \tilde{j}_i
	\end{equation}
	for all $i=p, p{-}1, \dots, 1$.
